Hydra Battles and Cie

### 2021-03-29 doc/chapter-primrec.tex
work on coqdoc comments

\section{First look at the Ackermann Library}

@@

\section{Basic Definitions}
\index{maths}{Primitive recursive functions}

@@

\begin{remark}
\label{projFunc-order-of-args}
Beware of the conventions used in the \texttt{primRec} library!
The constructor (\texttt{projFunc $n$ $m$})  is associated with the projection $\pi_{n-m,n}$ and \emph{not}
$\pi_{n, m}$.
For instance, the projection $\pi_{2,5}$ defined by $\pi_{2,5}(a,b,c,d,e)=b$ corresponds to the term
(\texttt{projFunc 5 3 H}), where \texttt{H} is a proof of $3<5$.
 This fact is reported in the comments of \texttt{primRec.v}. We presume that this convention makes it easier to define the evaluation function \texttt{evalProjFunc $n$} (see next sub-section) . Trying the other convention is left as an exercise.
\end{remark}

@@

\begin{Coqsrc}
Fixpoint evalPrimRec (n : nat) (f : PrimRec n) {struct f} : 
 naryFunc n :=
  match f in (PrimRec n) return (naryFunc n) with
  | succFunc => S
  | zeroFunc => 0
  | projFunc n m pf => evalProjFunc n m pf
  | composeFunc n m l f =>
      evalComposeFunc n m (evalPrimRecs _ _ l) (evalPrimRec _ f)
  | primRecFunc n g h =>
      evalPrimRecFunc n (evalPrimRec _ g) (evalPrimRec _ h)
  end

 with evalPrimRecs (n m : nat) (fs : PrimRecs n m) {struct fs} :
 Vector.t (naryFunc n) m :=
  match fs in (PrimRecs n m) return (Vector.t (naryFunc n) m) with
  | PRnil a => Vector.nil  (naryFunc a)
  | PRcons a b g gs =>
       Vector.cons _ (evalPrimRec _ g) _  (evalPrimRecs _ _ gs)
  end.
\end{Coqsrc}

@@

\begin{Coqsrc}
Example Ex1 : evalPrimRec 0 zeroFunc = 0.
Proof. reflexivity. Qed.

@@

Example Ex4 (x y z : PrimRec 2) (t: PrimRec 3):
  let u := composeFunc 2 3
                       (PRcons 2 2 x
                               (PRcons 2 1 y
                                       (PRcons 2 0 z
                                               (PRnil 2))))
                       t in
  let f := evalPrimRec 2 x in
  let g := evalPrimRec 2 y in
  let h := evalPrimRec 2 z in
  let i := evalPrimRec 3 t in
  let j := evalPrimRec 2 u in
  forall a b, j a b = i (f a b) (g a b) (h a b).
Proof. reflexivity. Qed.

>>>>

\section{First look at the Ackermann library}

@@

\section{Basic definitions}
\index{maths}{Primitive recursive functions}

@@

\begin{remark}
\label{projFunc-order-of-args}
Beware of the conventions used in the \texttt{primRec} library!
The constructor (\texttt{projFunc $n$ $m$})  is associated with the projection $\pi_{n-m,n}$ and \emph{not}
$\pi_{n, m}$.
For instance, the projection $\pi_{2,5}$ defined by $\pi_{2,5}(a,b,c,d,e)=b$ corresponds to the term
(\texttt{projFunc 5 3 H}), where \texttt{H} is a proof of $3<5$.
 This fact is reported in the comments of \texttt{primRec.v}. We presume that this convention makes it easier to define the evaluation function \texttt{evalProjFunc $n$} (see the next sub-section). Trying the other convention is left as an exercise.
\end{remark}

@@

\begin{Coqsrc}
Fixpoint evalPrimRec (n : nat) (f : PrimRec n) {struct f} : 
 naryFunc n :=
  match f in (PrimRec n) return (naryFunc n) with
  | succFunc => S
  | zeroFunc => 0
  | projFunc n m pf => evalProjFunc n m pf
  | composeFunc n m l f =>
      evalComposeFunc n m (evalPrimRecs _ _ l) (evalPrimRec _ f)
  | primRecFunc n g h =>
      evalPrimRecFunc n (evalPrimRec _ g) (evalPrimRec _ h)
  end
  with evalPrimRecs (n m : nat) (fs : PrimRecs n m) {struct fs} :
 Vector.t (naryFunc n) m :=
  match fs in (PrimRecs n m) return (Vector.t (naryFunc n) m) with
  | PRnil a => Vector.nil  (naryFunc a)
  | PRcons a b g gs =>
       Vector.cons _ (evalPrimRec _ g) _  (evalPrimRecs _ _ gs)
  end.
\end{Coqsrc}

@@

\vspace{4pt}
\noindent
\emph{From \href{../theories/html/hydras.MoreAck.PrimRecExamples.html}{MoreAck.PrimRecExamples}.}
\begin{Coqsrc}
Example Ex1 : evalPrimRec 0 zeroFunc = 0.
Proof. reflexivity. Qed.

@@

Example Ex4 (x y z : PrimRec 2) (t: PrimRec 3):
  let u := composeFunc 2 3
                       (PRcons 2 _ x
                               (PRcons 2 _ y
                                       (PRcons 2 _ z
                                               (PRnil 2))))
                       t in
  let f := evalPrimRec 2 x in
  let g := evalPrimRec 2 y in
  let h := evalPrimRec 2 z in
  let i := evalPrimRec 3 t in
  let j := evalPrimRec 2 u in
  forall a b, j a b = i (f a b) (g a b) (h a b).
Proof. reflexivity. Qed.
